### 2010-03-17 papers/icfp-2010-desc/paper_type_theory.tex
Desc@ICFP: uniformize spacing in arrays
Desc@ICFP: composed by -> composed of

\[
\begin{array}{l@{\;\;\Rightarrow\;\;}l}
\Gamma            \vdash \Bhab{t}{T}            
    & \Gamma \vdash \Valid\; \wedge\; \Gamma\vdash\Type{T} \\
\Gamma            \vdash s \equiv \Bhab{t}{T}   
    & \Gamma \vdash \Bhab{s}{T} \;\wedge\; \Gamma\vdash \Bhab{t}{T} \\
\Gamma ; \xS ; \Delta \vdash J                      
    & \Gamma \vdash \Bhab{s}{S} \;\Rightarrow\; 
          \Gamma ; \Delta[s/x] \vdash J[s/x] \\
\end{array}
\]

@@

We adapt and formalise this \emph{type propagation} mechanism to our
richer type theory. First of all, we define a high-level syntax,
composed by \emph{expressions}. Expressions are divided into two
syntactic categories: $\exprIn$ into which types are pushed in, and
$\exprEx$ from which types are pulled out. Following the bidirectional
presentation, $\exprIn$ are subject to type \emph{checking}, while
$\exprEx$ are subject to type \emph{synthesis}.

@@

A second consequence concerns the definition of a finite set. We can
abstract away the details of code and use a familiar syntax
instead. Hence, we use the syntax $[t_1 \ldots t_n]$ to denote the
finite sets composed by the named elements $t_1$, \ldots, $t_n$. The
translation to elements of $\EnumU$ is straightforward.

>>>>

\[
\begin{array}{l@{\;\Rightarrow\;\;}l}
\Gamma            \vdash \Bhab{t}{T}            
    & \Gamma \vdash \Valid\; \wedge\; \Gamma\vdash\Type{T} \\
\Gamma            \vdash s \equiv \Bhab{t}{T}   
    & \Gamma \vdash \Bhab{s}{T} \;\wedge\; \Gamma\vdash \Bhab{t}{T} \\
\Gamma ; \xS ; \Delta \vdash J                      
    & \Gamma \vdash \Bhab{s}{S} \;\Rightarrow\; 
          \Gamma ; \Delta[s/x] \vdash J[s/x] \\
\end{array}
\]

@@

We adapt and formalise this \emph{type propagation} mechanism to our
richer type theory. First of all, we define a high-level syntax,
composed of \emph{expressions}. Expressions are divided into two
syntactic categories: $\exprIn$ into which types are pushed in, and
$\exprEx$ from which types are pulled out. Following the bidirectional
presentation, $\exprIn$ are subject to type \emph{checking}, while
$\exprEx$ are subject to type \emph{synthesis}.

@@

A second consequence concerns the definition of a finite set. We can
abstract away the details of code and use a familiar syntax
instead. Hence, we use the syntax $[t_1 \ldots t_n]$ to denote the
finite sets composed of the named elements $t_1$, \ldots, $t_n$. The
translation to elements of $\EnumU$ is straightforward.
